Manuscript Figures for Genome Biology

### 2018-07-11 manuscript_figures/manuscript_figures.Rmd
Add summary figure for inf covar in casestudies

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "FDR",
                rowOrder = Fig4All.rowOrder, 
                annotate = "FDR", excludeMethods = NULL) +
          scale_fill_gradient2(high = "red", 
                         mid = "white", 
                         low = "blue", 
                         midpoint = alpha) +
  labs(fill = "Mean FDR")

@@

>>>>

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "FDR",
                rowOrder = Fig4All.rowOrder, 
                annotate = "FDR", excludeMethods = NULL) +
          scale_fill_gradient2(high = "darkred", 
                         mid = "white", 
                         low = "darkblue", 
                         midpoint = alpha) +
  labs(fill = "Mean FDR")

@@

# Informativeness of covariates in case studies

Here we create a heatmap similar to figure 4, but instead of containing the mean
proportion of maximum rejections, it plots the mean difference in the number of 
rejections using an informative covariate and the number of rejections using a 
random uninformative covariate, expressed as a proportion of the number of rejections
using the uninformative covariate. This is only created for those methods that
use an informative covariate.

# methods that use a covariate
cov.methods <- c("ihw", "bl", "lfdr", "scott-empirical", "scott-theoretical")

# regexp to construct master data table separating case study datasets, methods
# and covariates
obj.names <- str_split(objects, pattern = "/")
casestudy <- unlist(lapply(obj.names, function(x) x[3] ))
filename <- gsub(".rds", "", unlist(lapply(obj.names, function(x) x[4] )))
dataset <- unlist(lapply(str_split(filename, pattern = "-"), function(x) x[[1]]))
extD <- unlist(lapply(str_split(filename, pattern = "-"), function(x) x[[min(length(x), 2)]]))
extD <- gsub("samplesize", "n", extD)
extM <- unlist(lapply(str_split(filename, pattern = "-"), function(x) x[[min(length(x), 3)]]))
extC <- unlist(lapply(str_split(filename, pattern = "-"), function(x) x[[min(length(x), 4)]]))
inform <-  ifelse(grepl("uninf", objects), "uninf", "inf")
cov <- inform
df <- data.frame(filename, casestudy, dataset, inform, cov, stringsAsFactors = FALSE) %>%
  mutate(dataset = ifelse(grepl("enigma", dataset), paste(dataset, extD, sep="-"),
                          dataset)) %>%  
  mutate(dataset = ifelse(casestudy == "scRNAseq", paste(dataset, extM, sep="-"),
                          dataset)) %>%
  mutate(cov = ifelse(casestudy == "scRNAseq" & inform != "uninf", extC,  cov)) %>%
  mutate(cov = ifelse(casestudy == "ChIPseq" & inform != "uninf", "region-width",  cov)) %>%
  mutate(cov = ifelse(casestudy == "GSEA" & inform != "uninf", "set-size",  cov)) %>%
  mutate(cov = ifelse(casestudy == "GWAS" & inform != "uninf", extD,  cov)) %>%
  mutate(cov = ifelse(casestudy == "microbiome" & inform != "uninf", 
                      ifelse(grepl("abun", filename), "abundance", "ubiquity"),  cov))%>%
  mutate(cov = ifelse(casestudy == "RNAseq" & inform != "uninf", "mean",  cov))

tab <- tidy_df(objects=objects, colLabels=filename, 
              fill="meanRank", annotate=NULL, alpha =0.10) %>%
  rename(casestudy = "filename") %>%
  mutate(filename = gsub(".rds", "", filename))

dftab <- left_join(tab, df, by="filename") %>%
  filter(method %in% cov.methods) %>%
  select(filename, casestudy, dataset, method, cov, inform, nrejects) %>%
  mutate(id = paste(casestudy, dataset, method, sep = "-"))

uninftab <- dftab %>% 
  filter(inform == "uninf") %>%
  select(id, nrejects) %>%
  rename(nrejects = "uninf")

inftab <- dftab %>%
  filter(inform == "inf") %>%
  select(-inform)

rowOrder <- c("ihw", "bl", "lfdr", "scott-empirical", "scott-theoretical")

dftab <- left_join(inftab, uninftab, by = "id") %>%
  mutate(diff_inf = nrejects - uninf) %>%
  mutate(diff_inf_percent = diff_inf / nrejects) %>%
  mutate(method = factor(method, levels = rowOrder)) %>%
  group_by(casestudy, cov) %>%
  complete(method, dataset)

Fig_impactofinfcov <- ggplot(dftab, aes(x = dataset, y = method, fill = diff_inf_percent)) + 
        geom_raster() + 
        scale_fill_gradientn("% Increase\nin rejections",
                             labels = scales::percent, trans="log1p",
                             colours = c("darkblue","white","darkred"), 
                             values = scales::rescale(c(-.1,0,1)),
                             guide = "colorbar", limits=c(-.05,0.99)) +
        theme_bw() +
        xlab("Case Study") +
        ylab("Method") +
        facet_grid( ~ casestudy + cov, scales = "free", space = "free") +
        ggtitle("Impact of informative covariate on number of rejections") +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.985, 0.91), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 9),
              legend.margin = margin(6, 10, 6, 10))

Fig_impactofinfcov
ggsave(file.path(outdir, "Figure_impactofinfcov.pdf"), width = 15, height = 4.25)
```
